---
title: 'Python Geographic Data Visualization'
author: ' '
date: '2019-11-28'
slug: pygeo
---

```{r,include=F}
knitr::opts_chunk$set(comment=NA,error=T,message = F,warning = F,fig.align='center',out.width ='100%')
```

A very simple example to show how to plot a scatter map using Python [geopandas](http://geopandas.org/) library. The data is from this [link](https://wp-contents.netlify.com/data/earthquake20190630.csv). Attention that some columns' names are Chinese characters. I give methods to change those names below.


```python
import os
import pandas as pd    
import numpy as np
import seaborn as sns
import matplotlib.pyplot as plt
import geopandas as gp
sns.set_style("whitegrid")
```


```python
%matplotlib inline
%config InlineBackend.figure_format = 'svg'
```


```python
world = gp.read_file(gp.datasets.get_path('naturalearth_lowres'))
```


```python
earthquake = pd.read_csv("E:\\MaLearning\\earthquake20190630.csv",encoding = 'gb18030') 
```


```python
earthquake.head()
```




<div>
<style scoped>
    .dataframe tbody tr th:only-of-type {
        vertical-align: middle;
    }

    .dataframe tbody tr th {
        vertical-align: top;
    }

    .dataframe thead th {
        text-align: right;
    }
</style>
<table border="1" class="dataframe">
  <thead>
    <tr style="text-align: right;">
      <th></th>
      <th>发震时刻</th>
      <th>震级(M)</th>
      <th>纬度(°)</th>
      <th>经度(°)</th>
      <th>深度(千米)</th>
      <th>参考位置</th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <th>0</th>
      <td>2019-06-30 21:44:44</td>
      <td>3.0</td>
      <td>27.56</td>
      <td>112.10</td>
      <td>6.0</td>
      <td>湖南娄底市双峰县</td>
    </tr>
    <tr>
      <th>1</th>
      <td>2019-06-30 21:32:29</td>
      <td>3.1</td>
      <td>28.44</td>
      <td>104.81</td>
      <td>8.0</td>
      <td>四川宜宾市长宁县</td>
    </tr>
    <tr>
      <th>2</th>
      <td>2019-06-30 12:14:25</td>
      <td>3.0</td>
      <td>28.43</td>
      <td>104.77</td>
      <td>9.0</td>
      <td>四川宜宾市珙县</td>
    </tr>
    <tr>
      <th>3</th>
      <td>2019-06-30 03:44:11</td>
      <td>4.8</td>
      <td>22.43</td>
      <td>122.31</td>
      <td>30.0</td>
      <td>台湾台东县海域</td>
    </tr>
    <tr>
      <th>4</th>
      <td>2019-06-30 03:09:29</td>
      <td>3.1</td>
      <td>31.00</td>
      <td>98.96</td>
      <td>7.0</td>
      <td>四川甘孜州白玉县</td>
    </tr>
  </tbody>
</table>
</div>




```python
colname = ['Time','Degree','latitude(°)', 'longitude(°)',
           'depth(km)', 'position']
newdata = np.array(earthquake)
earthquake2 = pd.DataFrame(newdata,columns = colname)
earthquake2.head()
```




<div>
<style scoped>
    .dataframe tbody tr th:only-of-type {
        vertical-align: middle;
    }

    .dataframe tbody tr th {
        vertical-align: top;
    }

    .dataframe thead th {
        text-align: right;
    }
</style>
<table border="1" class="dataframe">
  <thead>
    <tr style="text-align: right;">
      <th></th>
      <th>Time</th>
      <th>Degree</th>
      <th>latitude(°)</th>
      <th>longitude(°)</th>
      <th>depth(km)</th>
      <th>position</th>
    </tr>
  </thead>
  <tbody>
    <tr>
      <th>0</th>
      <td>2019-06-30 21:44:44</td>
      <td>3</td>
      <td>27.56</td>
      <td>112.1</td>
      <td>6</td>
      <td>湖南娄底市双峰县</td>
    </tr>
    <tr>
      <th>1</th>
      <td>2019-06-30 21:32:29</td>
      <td>3.1</td>
      <td>28.44</td>
      <td>104.81</td>
      <td>8</td>
      <td>四川宜宾市长宁县</td>
    </tr>
    <tr>
      <th>2</th>
      <td>2019-06-30 12:14:25</td>
      <td>3</td>
      <td>28.43</td>
      <td>104.77</td>
      <td>9</td>
      <td>四川宜宾市珙县</td>
    </tr>
    <tr>
      <th>3</th>
      <td>2019-06-30 03:44:11</td>
      <td>4.8</td>
      <td>22.43</td>
      <td>122.31</td>
      <td>30</td>
      <td>台湾台东县海域</td>
    </tr>
    <tr>
      <th>4</th>
      <td>2019-06-30 03:09:29</td>
      <td>3.1</td>
      <td>31</td>
      <td>98.96</td>
      <td>7</td>
      <td>四川甘孜州白玉县</td>
    </tr>
  </tbody>
</table>
</div>




```python
world.plot(color='white', edgecolor='black',figsize=(11,9))
sns.scatterplot(x='longitude(°)',
y='latitude(°)',linewidth=0,data=earthquake2,s=3, color='red')
```




    <matplotlib.axes._subplots.AxesSubplot at 0x230b317bb38>



```{r,echo=F,fig.cap='A map shows earthquakes happened worldwide during 2017-2019'}
knitr::include_graphics('/img/vignette/geo.svg')
```

